Tutorial_4

### 2024-12-16 Tutorial_4.Rmd
removed unnecessary text

## read in the data from the OSF and store it in a relevant folder
osf_sim1_data <-
  # retrieve the OSF (main) project
  osf_retrieve_node("3dbcs") %>% ## this is just one project picked at random
  # list files in this repository - there must be a more efficient way than this...
  osf_ls_files(pattern = "Tutorial_4_planning") %>%
  osf_ls_files(pattern = "data") %>%
  osf_ls_files(pattern = "sim1") %>%
  osf_ls_files(pattern = "sim1_data") %>%
  osf_download(path = "./Tutorial_4_planning/data/sim1/")
```

@@

## read in the data from the OSF and store it in a relevant folder
osf_sim2_data <-
  # retrieve the OSF (main) project
  osf_retrieve_node("3dbcs") %>% ## this is just one project picked at random
  # list files in this repository - there must be a more efficient way than this...
  osf_ls_files(pattern = "Tutorial_4_planning") %>%
  osf_ls_files(pattern = "data") %>%
  osf_ls_files(pattern = "sim2") %>%
  osf_ls_files(pattern = "sim2_data") %>%
  osf_download(path = "./Tutorial_4_planning/data/sim2/")
```

>>>>

## read in the data from the OSF and store it in a relevant folder
osf_sim1_data <-
  # retrieve the OSF (main) project
  osf_retrieve_node("3dbcs") %>% 
  # list files in this repository - there must be a more efficient way than this...
  osf_ls_files(pattern = "Tutorial_4_planning") %>%
  osf_ls_files(pattern = "data") %>%
  osf_ls_files(pattern = "sim1") %>%
  osf_ls_files(pattern = "sim1_data") %>%
  osf_download(path = "./Tutorial_4_planning/data/sim1/")
```

@@

## read in the data from the OSF and store it in a relevant folder
osf_sim2_data <-
  # retrieve the OSF (main) project
  osf_retrieve_node("3dbcs") %>% 
  # list files in this repository - there must be a more efficient way than this...
  osf_ls_files(pattern = "Tutorial_4_planning") %>%
  osf_ls_files(pattern = "data") %>%
  osf_ls_files(pattern = "sim2") %>%
  osf_ls_files(pattern = "sim2_data") %>%
  osf_download(path = "./Tutorial_4_planning/data/sim2/")
```
